---
title: "P8105_homework1_gl2677"
author: Gaotong LIU (gl2677)
date: 2019-09-20
output: github_document
editor_options: 
  chunk_output_type: console
---
# Problem 1
## Section 1
Here is a **code chunk** that creates the data frame comprised of:

*   A random sample of size 8 from a standard Normal distribution
*   A logical vector indicating whether elements of the sample are greater than 0
*   A character vector of length 8
*   A factor vector of length 8, with 3 different factor “levels”

```{r data_frame_1, message=FALSE}
library(tidyverse)

sample = rnorm(8)
vec_numeric = sample
vec_logical = sample > 0
vec_char = c("My","name","is","Gaotong","LIU","MS","Biostatistic","T & M")
vec_factor = factor(c("High","Low","Medium","High","High","Low","Medium","Low"))
                    
df_1 = tibble(vec_numeric ,vec_logical ,vec_char ,vec_factor)
```

I try to take the mean of the variables:

The mean of `vec_numeric` is `r mean (vec_numeric)`.
The mean of `vec_logical` is `r mean (vec_logical)`.
The mean of `vec_char` is `r mean (vec_char)`.
The mean of `vec_factor` is `r mean (vec_factor)`.

Therefore, only numeric and logical variables work for `mean()`.

## Section 2

```{r convert_variable, eval=FALSE}
as.numeric(vec_logical)
as.numeric(vec_char)
as.numeric(vec_factor)

as.numeric(vec_logical) * sample
as.factor(vec_logical) * sample
as.numeric(as.factor(vec_logical)) * sample
```

`vec_logical` logical variables can be converted to numeric values, T = 1, F = 0.
`vec_char` charcter variables can **not** be converted to numberic variables, so there is no way to take the mean of character variables.
`vec_factor` factor variables can be converted to numeric variables corresponding to levels, but these numeric variables can **not** do basic computations.Therefore, factor variables do not work for `mean()`.

# Problem 2
## Section 1
Here is a **code chunk** that creates the data frame comprised of:

* x: a random sample of size 500 from a standard Normal distribution
* y: a random sample of size 500 from a standard Normal distribution
* A logical vector indicating whether x + y > 1
* A numeric vector created by coercing the above logical vector
* A factor vector created by coercing the above logical vector

```{r data_frame_2}
x = rnorm(500)
y = rnorm(500)
vec_logical_2 = x + y > 1
vec_numeric_2 = as.numeric(vec_logical_2)
vec_factor_2 = as.factor(vec_logical_2)
df_2 = tibble(x, y, vec_logical_2, vec_numeric_2, vec_factor_2)

```

The data frame has `r nrow(df_2)` rows and `r ncol(df_2)` columns. The mean of `x` is `r mean(x)`, and the median of `x` is `r median(x)`, and the stardar deviation of `x` is `r sd(x)`. The proportion of cases for which ` x + y > 1 ` is `r sum(vec_logical_2)/length(vec_logical_2)`.

```{r}
df_2 %>% ggplot(aes(x = x, y = y, color = vec_logical_2)) +
  geom_point()
ggsave("scatterplot_logical.pdf")

df_2 %>% ggplot(aes(x = x, y = y, color = vec_numeric_2)) +
  geom_point()
df_2 %>% ggplot(aes(x = x, y = y, color = vec_factor_2)) +
  geom_point()
```

The color scales of logical variables and factor variables are the same, which contain only two categories. The color scale of numeric variables is color plaette.

















